column underneath i.e. day column has =day(b1:b15) \item #VALUE! appears in the formula cell. \item Leaving for now. \end{itemize} Dates
as Data (Attempt 2) \begin{itemize} \item Opened new spreadsheet \item Remembered to create a new tab rather than to manipulate the raw
data \item Copied interview dates into column A in new tab \item Named column B - Day, column C - month and column D - year \item Entered
the formula =day(A2) into B2 -\textbf{ SUCCESS} \item Clicked and dragged the bottom right corner of cell B2 down entire column \item Day
column has now extracted the dates correctly. \item Copying process with month and year column -\textbf{SUCCESS} \item Adding 17/11 in
cell A16, automates to 17-Nov in interview date section and includes the year 2019 in the column \item If no year is specified the current
year must be inserted. \item End of dates as data exercise. \end{itemize} \subsection{Final Thoughts} \textbf{8:30pm} Very frustrating
that what was assumed as a simple task has taken a lot of back and forth and time but hoping once I'm able to reiterate these errors with
someone it will be clear and straight forward. \textbf{9:22pm} After reading through other learning journals and it became a lot clearer
the mistakes I was making. I wish there were clearer instructions in these sites to assist with novice users such as myself. I am glad
that I was able to successfully complete the exercise after seeing similar steps. This task reminded me that I must use a new tab when
adding and working with data in excel. \end{document}
